---
title: "draft_final"
author: "Maggie Head"
date: "2/15/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(tidyverse)
library(haven)
library(lm.beta)
library(rstatix)
library(colorspace)
library(ggrepel)
```


# Data Preparation for First Plot

```{r data_weightgoal, echo=TRUE}
weight2011 <- here::here("data", "2011_weight_history.XPT") %>%
  read_xpt()

dep2011 <-  here::here("data", "2011_depression_screener.XPT") %>%
  read_xpt()

demo2011 <- here::here("data", "2011_demographics.XPT") %>%
  read_xpt()

dep1 <- left_join(weight2011,dep2011)
dep <- left_join(dep1, demo2011)

#removing "refuse to answer"
dep <- dep %>%
  filter((WHD020 != 7777 & WHD020 != 9999), 
         (WHD045 != 77777 & WHD045 != 99999))

#new variables: depression mean 

dep <- dep %>%
  rowwise() %>%
  mutate(dpq = sum(c(DPQ010, DPQ020, DPQ030, DPQ040, DPQ050,
                        DPQ060, DPQ070, DPQ080,DPQ090, DPQ100)))%>%
  drop_na(dpq)


#actual-ideal weight discrepency variable
dep <- dep %>%
  mutate(dif_weight = WHD045 - WHD020)
summary(dep$dif_weight)

#removing men 
dep_filtered <- dep %>%
  filter(RIAGENDR == 2,
         dif_weight <=0)%>%
  mutate(mean_dpq = mean(dpq))
summary(dep_filtered$dif_weight)


```

# Draft of First Plot 


```{r plot_weightgoaldraft,echo=TRUE}
dep_filtered %>%
  ggplot(aes(dif_weight,dpq)) +
  geom_col() +
  scale_x_reverse()
    labs(x = "Desired Weight Loss Goal (in pounds)",
         y = "Depressive Symptoms",
       title = "Depressive Symptoms",
       subtitle = "According to Desired Weight Loss")
```
# Continuing First Plot 


```{r plot_weightgoal, echo=TRUE}
#creating factor variable for actual-ideal weight

dep$dif_weight_fct <-Hmisc::cut2(dep$dif_weight,c(-125,-100, -75,
                                                  -50, -25))
summary(dep$dif_weight_fct)
dep$dif_weight_fct <- as.factor(dep$dif_weight_fct)
levels(dep$dif_weight_fct)

#githubtest
#testing again

#renaming levels
dep_lev <- dep %>%
  mutate(dif_weight_fct = fct_recode(dif_weight_fct, 
                  "More than 125 lbs" = "[-240,-125)", 
                  "100-125" = "[-125,-100)",
                  "75-100" = "[-100, -75)",
                  "50-75" = "[ -75, -50)",
                  "25-50" = "[ -50, -25)",
                  "0-25" = "[ -25, 100]"))

#mean by factor
plot1_df <-dep_lev %>%
  group_by(dif_weight_fct) %>%
  summarise(group_dpq = mean(dpq),
            group_se = sd(dpq)/sqrt(n()))


#plot

plot1_df %>%
  ggplot(aes(group_dpq, dif_weight_fct)) +
  geom_errorbarh(aes(xmin =  group_dpq - 1.96*group_se,
     xmax = group_dpq+ 1.96*group_se),
     height = .5) +
  geom_point() +
  labs(x = "Severity of Depressive Symptomatology",
         y = "Desired Weight Loss Goal (in pounds)",
       title = "Depressive Symptoms",
       subtitle = "According to Desired Weight Loss",
       caption = "Data from the 2011 National Health and Nutrition Examination Survey") +
  theme_minimal()


```


# Draft 3 of Weight Plot



```{r weightplot_draft3, echo=TRUE}
plot1_df %>%
  ggplot(aes(group_dpq, dif_weight_fct)) +
  geom_errorbarh(aes(xmin =  group_dpq - 1.96*group_se,
     xmax = group_dpq+ 1.96*group_se),
     color = "thistle",
     height = .2) +
  geom_errorbarh(aes(xmin = group_dpq + qnorm(.025)*group_se,
                    xmax = group_dpq + qnorm(.975)*group_se),
                color = "cadetblue2",
                height = 0.2,
                size = 0.5) + # 95% CI
  geom_errorbarh(aes(xmin = group_dpq + qnorm(.05)*group_se,
                    xmax = group_dpq + qnorm(.95)*group_se),
                color = lighten("darkolivegreen2", .1),
                height = 0.2,
                size = 0.8) + # 90% CI
  geom_errorbarh(aes(xmin = group_dpq + qnorm(.1)*group_se,
                    xmax = group_dpq + qnorm(.9)*group_se),
                color = "darkolivegreen3",
                height = 0.2,
                size = 1.1) +
  geom_point() +
  labs(x = "Severity of Depressive Symptomatology",
         y = "Desired Weight Loss Goal (in pounds)",
       title = "Depressive Symptoms",
       subtitle = "According to Desired Weight Loss",
       caption = "Data from the 2011 National Health and Nutrition Examination Survey") +
  theme_minimal()
```



# Data Prep for Second Plot


```{r data_secure, echo=TRUE}
secure2015 <- here::here("data", "2015_food_security.XPT") %>%
  read_xpt()

dep2015 <-  here::here("data", "2015_depression_screener.XPT") %>%
  read_xpt()

secure_dep <- left_join(secure2015, dep2015)


secure_dep <- secure_dep %>%
  rowwise() %>%
  mutate(dpq_sum = sum(c(DPQ010, DPQ020, DPQ030, DPQ040, DPQ050,
                        DPQ060, DPQ070, DPQ080,DPQ090, DPQ100))) %>%
  drop_na(dpq_sum)

secure_group <- secure_dep %>%
  group_by(FSDHH) %>%
  summarise(dpq_group = mean(dpq_sum))



#examining relationship
secure_dep$FSDHH <- as.factor(secure_dep$FSDHH)
secure_mod <- lm(dpq_sum ~ FSDHH, secure_dep)
summary(secure_mod)

secure_group$FSDHH <- as.factor(secure_group$FSDHH)
```

# Draft of Second Plot

```{r secure_plot_draft}
#plot
secure_group %>%
  ggplot() +
  geom_col(aes(FSDHH,dpq_group)) +
  labs(x ="Level of Food Insercurity",
       y = "Severity of Depresive Symptomatology")
```

# Second Plot Continued



```{r securedepress_plot, echo=TRUE}
#plot

#removing NA group
secure_group <- secure_group[-5,]

secure_group %>%
  ggplot() +
  geom_col(aes(FSDHH,dpq_group, fill = FSDHH), alpha = .8,
           show.legend = F) +
  labs(x ="Level of Food Insercurity (per household)",
       y = "Average Depresive Symptomatology",
       title = "Depressive Symptoms by Food Security Level",
       caption ="Data from the 2015 National Health and Nutrition Examination Survey")+
  scale_x_discrete(breaks = c(1,2,3,4),
                   labels = c("1" = "Full",
                            "2" = "Marginal",
                            "3" = "Low",
                            "4" = "Very Low"))+
  scale_fill_brewer(palette = "Set3")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank())


```


# Continuing Draft



```{r securedepress_plotdraft3, echo=TRUE}

secure_group %>%
  ggplot() +
  geom_col(aes(FSDHH,dpq_group, fill = FSDHH), alpha = .8,
           show.legend = F) +
  geom_text(aes(FSDHH,dpq_group, label = paste0(round(dpq_group,2))), 
            nudge_y = .4, size = 4)+
  labs(x ="Level of Food Insercurity (per household)",
       y = "Average Depresive Symptomatology",
       title = "Depressive Symptoms by Food Security Level",
       caption ="Data from the 2015 National Health and Nutrition Examination Survey")+
  scale_x_discrete(breaks = c(1,2,3,4),
                   labels = c("1" = "Full",
                            "2" = "Marginal",
                            "3" = "Low",
                            "4" = "Very Low"))+
  scale_fill_brewer(palette = "Set3")+
  theme_minimal()+
  coord_flip()+
  theme(panel.grid.major.x = element_blank())


```


# Data Prep for Third Plot 

```{r securetrends, echo=TRUE}
weight2003 <- here::here("data", "2003_weight_history.XPT") %>%
  read_xpt()

weight2005 <- here::here("data", "2005_weight_history.XPT") %>%
  read_xpt()

weight2007 <- here::here("data", "2007_weight_history.XPT") %>%
  read_xpt()

weight2009 <- here::here("data", "2009_weight_history.XPT") %>%
  read_xpt()

weight2013 <- here::here("data", "2013_weight_history.XPT") %>%
  read_xpt()

weight2015 <- here::here("data", "2015_weight_history.XPT") %>%
  read_xpt()

###foodinsecure

food2003 <- here::here("data", "2003_food_security.XPT") %>%
  read_xpt()

food2005 <- here::here("data", "2005_food_security.XPT") %>%
  read_xpt()

food2007 <- here::here("data", "2007_food_security.XPT") %>%
  read_xpt()

food2009 <- here::here("data", "2009_food_security.XPT") %>%
  read_xpt()

food2011 <- here::here("data", "2011_food_security.XPT") %>%
  read_xpt()

food2013 <- here::here("data", "2013_food_security.XPT") %>%
  read_xpt()

food2015 <- here::here("data", "2015_food_security.XPT") %>%
  read_xpt()

#joining
yr2005 <- left_join(weight2005, food2005)
yr2007 <- left_join(weight2007, food2007)
yr2009 <- left_join(weight2009, food2009)
yr2011 <- left_join(weight2011, food2011)
yr2013 <- left_join(weight2013, food2013)
yr2015 <- left_join(weight2015, food2015)

#adding years, narrowing data


yr2005<- yr2005 %>%
  add_column(year = 2005) %>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)

yr2007 <- yr2007 %>%
  add_column(year = 2007)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)

yr2009 <- yr2009 %>%
  add_column(year = 2009)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)

yr2011 <- yr2011 %>%
  add_column(year = 2011)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)

yr2013 <- yr2013 %>%
  add_column(year = 2013)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)

yr2015 <- yr2015%>%
  add_column(year = 2015)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, year, FSDAD)




full_yr <- yr2015 %>%
  add_row(yr2005) %>%
  add_row(yr2007) %>%
  add_row(yr2009) %>%
  add_row(yr2011) %>%
  add_row(yr2013)
    
#recoding: 1 = presence of ed behavior    
full_yr$WHD080A[which(!is.na(full_yr$WHD080A))] <-1    
full_yr$WHD080C[which(!is.na(full_yr$WHD080C))] <-1  
full_yr$WHD080E[which(!is.na(full_yr$WHD080E))] <-1  
full_yr$WHD080G[which(!is.na(full_yr$WHD080G))] <-1  
full_yr$WHD080J[which(!is.na(full_yr$WHD080J))] <-1  
full_yr$WHD080K[which(!is.na(full_yr$WHD080K))] <-1  
full_yr$WHD080M[which(!is.na(full_yr$WHD080M))] <-1  
full_yr$WHD080O[which(!is.na(full_yr$WHD080O))] <-1  

#create ed composite   
full_yr <- full_yr %>%
  rowwise() %>%
  mutate(ed_sum = sum(WHD080A, WHD080C, WHD080E,
                        WHD080G, WHD080J, WHD080K,
                        WHD080M, WHD080O, na.rm = T))

full_df <- full_yr %>%
  group_by(FSDHH, year) %>%
  summarise(ed_mean = mean(ed_sum, na.rm = T))

full_df <- full_df[-c(25:30),]

full_df$FSDHH<- as.factor(full_df$FSDHH)  


#testing model
full_yr$FSDHH <- as.factor(full_yr$FSDHH)  
full_yr <- full_yr %>%
  rowwise() %>%
  mutate(ed_mean = mean(ed_sum, na.rm = T))

```


# Draft of Third Plot 

```{r secure-raceplot_draft, echo=TRUE}
#plot2
full_df %>%
  ggplot(aes(year, ed_mean)) +
  geom_point(aes(color = FSDHH))+
  labs(x = "Year",
       y = "Disordered Eating Symptoms",
       title = "Disordered Eating Symptoms by Food Security Group",
       color = "Food Security Level") 
```

# Third Plot Continued 

```{r secure-raceplot, echo=TRUE}
#recoding factors, creating percentage
full_yr_grouped <- full_df %>%
  mutate(FSDHH = fct_recode(FSDHH,
                            "Full" = "1",
                            "Marginal" = "2",
                            "Low" = "3",
                            "Very Low" = "4"),
         ed_mean = ed_mean/5)

#plot2
full_yr_grouped %>%
  ggplot(aes(year, ed_mean)) +
  geom_point(aes(color = FSDHH))+
  geom_line(aes(color = FSDHH))+
  scale_x_continuous(breaks = c(2005,2007,2009,2011,2013,2015),
                     labels = c(2005,2007,2009,2011,2013,2015))+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "Year",
       y = "Proportion of Engagement \nin Disordered Eating Symptoms(%)",
       title = "Trends in Disordered Eating Symptoms",
       subtitle = "According to Food Security Level",
       color = "Food Security Level") +
  theme_minimal()
```


# And Continuing 

```{r plot3_draft3, echo=TRUE}

full_yr_grouped %>%
  ggplot(aes(year, ed_mean)) +
  geom_point(aes(color = FSDHH), show.legend = F)+
  geom_line(aes(color = FSDHH), show.legend = F)+
  scale_x_continuous(breaks = c(2005,2007,2009,2011,2013,2015),
                     labels = c(2005,2007,2009,2011,2013,2015),
                     limits = c(2005,2017.2))+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "Year",
       y = "Proportion of Sample Engagement \nin Disordered Eating Symptoms(%)",
       title = "Trends in Disordered Eating Symptoms",
       subtitle = "According to Food Security Level",
       color = "Food Security Level",
       caption = "Data from the National Health and Nutrition Examination Survey 2005-2015") +
  geom_text_repel(data = filter(full_yr_grouped, year == "2015"),
            aes(y = ed_mean, label = FSDHH, color = FSDHH),show.legend = F,nudge_x = 5, segment.linetype = "dashed", segment.size = .2)+
  theme_minimal()
```


# Data Preparation for Fourth Plot

```{r tile_data, echo=TRUE}
demo2015 <- here::here("data", "2015_demographics.XPT") %>%
  read_xpt()

weight2015 <- here::here("data", "2015_weight_history.XPT") %>%
  read_xpt()

food2015 <- here::here("data", "2015_food_security.XPT") %>%
  read_xpt()

foodwt15 <- left_join(weight2015, food2015)
race_full <- left_join(foodwt15, demo2015)

race_full <- race_full %>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, FSDHH, FSDAD, 
        INDFMIN2, INDFMPIR, INDHHIN2, RIDRETH3, SEQN)

#recoding ED behaviors
race_full$WHD080A[which(!is.na(race_full$WHD080A))] <-1    
race_full$WHD080C[which(!is.na(race_full$WHD080C))] <-1  
race_full$WHD080E[which(!is.na(race_full$WHD080E))] <-1  
race_full$WHD080G[which(!is.na(race_full$WHD080G))] <-1  
race_full$WHD080J[which(!is.na(race_full$WHD080J))] <-1  
race_full$WHD080K[which(!is.na(race_full$WHD080K))] <-1  
race_full$WHD080M[which(!is.na(race_full$WHD080M))] <-1  
race_full$WHD080O[which(!is.na(race_full$WHD080O))] <-1  



race_summ <- race_full %>%
  group_by(RIDRETH3, FSDHH) %>%
  summarise(freq1 = sum(WHD080A, na.rm = T)/n(),
            freq2 = sum(WHD080C, na.rm = T)/n(),
            freq3 = sum(WHD080E, na.rm = T)/n(),
            freq4 = sum(WHD080G, na.rm = T)/n(),
            freq5 = sum(WHD080J, na.rm = T)/n(),
            freq6 = sum(WHD080K, na.rm = T)/n(),
            freq7 = sum(WHD080M, na.rm = T)/n(),
            freq8 = sum(WHD080O, na.rm = T)/n())

long <- race_summ %>%
  pivot_longer(!c(FSDHH, RIDRETH3), 
                  names_to = "behavior", 
                  values_to = "frequency")

#recoding factors 


long_plot_draft <- long %>%
  mutate_at(c("FSDHH", "RIDRETH3","behavior"), as.factor) %>%
  mutate(FSDHH = fct_recode(FSDHH,
                            "Full" = "1",
                            "Marginal" = "2",
                            "Low" = "3",
                            "Very Low" = "4"))

```


# Draft of Fourth Plot 

```{r plot3_draft}
long_plot_draft %>%
  ggplot(aes(behavior, FSDHH)) +
  geom_tile(aes(fill = frequency)) +
  facet_wrap(~RIDRETH3) +
  labs(x = "Disordered Behavior",
       y = "Food Security Level",
       title = "Frequency of Disordered Eating Behaviors",
       subtitle = "By Racial Identity and Food Security Level")
```

# Fourth Plot 

```{r plot4, fig.height=10, fig.width=4}
#recoding factors 


long_plot <- long %>%
  mutate_at(c("FSDHH", "RIDRETH3","behavior"), as.factor) %>%
  mutate(FSDHH = fct_recode(FSDHH,
                            "Full" = "1",
                            "Marginal" = "2",
                            "Low" = "3",
                            "Very Low" = "4"),
         RIDRETH3 = fct_recode(RIDRETH3, 
                  "Mexican American" = "1",
                  "Other Hispanic" = "2",
                  "Non-Hispanic White" = "3",
                  "Non-Hispanic Black" = "4",
                  "Non-Hispanic Asian" = "6",
                  "Other Race/Multiracial" = "7"),
         behavior = fct_recode(behavior,
                               "Ate Less Overall" = "freq1",
                               "Ate Less Fat" = "freq2",
                               "Skipped Meals" = "freq3",
                               "Liquid Diet" = "freq4",
                               "nonRx Diet Pills" = "freq5",
                               "Purging" = "freq6",
                               "Water Loading" = "freq7",
                               "Carb Restriction" = "freq8")) %>%
  drop_na()

long_plot %>%
  ggplot(aes(behavior, FSDHH)) +
  geom_tile(aes(fill = frequency), color = "white") +
  facet_wrap(~RIDRETH3,nrow =3) +
  labs(x = "Disordered Eating Behavior",
       y = "Food Security Level",
       fill = "Frequency", 
       title = "Frequency of Disordered Eating Behaviors",
       subtitle = "According to Racial Identity and Food Security Level",
       caption = "Data from the 2015 National Health and Nutrition Examination Survey") +
  coord_flip()+
  scale_fill_viridis_c(option="magma")+
  theme_minimal()


```

# Next Draft

```{r plot4_draft3, echo=TRUE}
long_plot %>%
  ggplot(aes(behavior, FSDHH)) +
  geom_tile(aes(fill = frequency), color = "white") +
  facet_wrap(~RIDRETH3,nrow =3) +
  labs(x = "Disordered Eating Behavior",
       y = "Food Security Level",
       fill = "Frequency", 
       title = "Frequency of Disordered Eating Behaviors",
       subtitle = "According to Racial Identity and Food Security Level",
       caption = "Data from the 2015 National Health and Nutrition Examination Survey") +
  coord_flip()+
  scale_fill_viridis_c(option="magma", labels = scales::percent)+
  theme_minimal() +
  theme(plot.caption.position = "plot")
```




# Data Preparation of Fifth Plot

```{r racetrends_data}
weight2003 <- here::here("data", "2003_weight_history.XPT") %>%
  read_xpt()

weight2005 <- here::here("data", "2005_weight_history.XPT") %>%
  read_xpt()

weight2007 <- here::here("data", "2007_weight_history.XPT") %>%
  read_xpt()

weight2009 <- here::here("data", "2009_weight_history.XPT") %>%
  read_xpt()

weight2013 <- here::here("data", "2013_weight_history.XPT") %>%
  read_xpt()

weight2015 <- here::here("data", "2015_weight_history.XPT") %>%
  read_xpt()

###demographics

demo2005 <- here::here("data", "2005_demographics.XPT") %>%
  read_xpt()

demo2007 <- here::here("data", "2007_demographics.XPT") %>%
  read_xpt()

demo2009 <- here::here("data", "2009_demographics.XPT") %>%
  read_xpt()

demo2011 <- here::here("data", "2011_demographics.XPT") %>%
  read_xpt()

demo2013 <- here::here("data", "2013_demographics.XPT") %>%
  read_xpt()

demo2015 <- here::here("data", "2015_demographics.XPT") %>%
  read_xpt()


#joining
year1 <- left_join(weight2005, demo2005)
year2 <- left_join(weight2007, demo2007)
year3 <- left_join(weight2009, demo2009)
year4 <- left_join(weight2011, demo2011)
year5 <- left_join(weight2013, demo2013)
year6 <- left_join(weight2015, demo2015)

#creating full years

year1<- year1 %>%
  add_column(year = 2005) %>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, RIDRETH1, year)

year2 <- year2 %>%
  add_column(year = 2007)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O,RIDRETH1, year)

year3 <- year3 %>%
  add_column(year = 2009)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, RIDRETH1, year)

year4 <- year4 %>%
  add_column(year = 2011)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, RIDRETH1, year)

year5 <- year5 %>%
  add_column(year = 2013)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, RIDRETH1, year)

year6 <- year6%>%
  add_column(year = 2015)%>%
    select(WHD080A, WHD080C, WHD080E,
        WHD080G, WHD080J, WHD080K,
         WHD080M, WHD080O, RIDRETH1, year)


race_weight <- year6 %>%
  add_row(year5) %>%
  add_row(year4) %>%
  add_row(year3) %>%
  add_row(year2) %>%
  add_row(year1)

#recoding: 1 = presence of ed behavior    
race_weight$WHD080A[which(!is.na(race_weight$WHD080A))] <-1    
race_weight$WHD080C[which(!is.na(race_weight$WHD080C))] <-1  
race_weight$WHD080E[which(!is.na(race_weight$WHD080E))] <-1  
race_weight$WHD080G[which(!is.na(race_weight$WHD080G))] <-1  
race_weight$WHD080J[which(!is.na(race_weight$WHD080J))] <-1  
race_weight$WHD080K[which(!is.na(race_weight$WHD080K))] <-1  
race_weight$WHD080M[which(!is.na(race_weight$WHD080M))] <-1  
race_weight$WHD080O[which(!is.na(race_weight$WHD080O))] <-1  


#create ed composite   
race_weight<- race_weight %>%
  rowwise() %>%
  mutate(ed_sum = sum(WHD080A, WHD080C, WHD080E,
                        WHD080G, WHD080J, WHD080K,
                        WHD080M, WHD080O, na.rm = T))

race_weight_group <- race_weight %>%
  group_by(RIDRETH1, year) %>%
  summarise(ed_mean_race = mean(ed_sum, na.rm = T))
```

# Draft of Fifth Plot

```{r raceplot_draft, echo=TRUE}
race_weight_group$RIDRETH1 <- as.factor(race_weight_group$RIDRETH1)


#plot draft
race_weight_group %>%
  ggplot(aes(year, ed_mean_race)) +
  geom_line(aes(color = RIDRETH1)) +
  labs(x = "Year",
       y = "Mean of Disordered Eating Symptoms")
  
```

# Fifth Plot 

```{r raceplot, echo=TRUE}
race_weight_group$RIDRETH1 <- as.factor(race_weight_group$RIDRETH1)

race_weight_labeled <- race_weight_group %>%
  mutate(RIDRETH1 = fct_recode(RIDRETH1, 
                  "Mexican American" = "1",
                  "Other Hispanic" = "2",
                  "Non-Hispanic White" = "3",
                  "Non-Hispanic Black" = "4",
                  "Other Race/Multiracial" = "5"),
         ed_mean_race = ed_mean_race/5)


race_weight_labeled %>%
  ggplot(aes(year, ed_mean_race)) +
  geom_point(aes(color = RIDRETH1))+
  geom_line(aes(color = RIDRETH1)) +
  scale_x_continuous(breaks = c(2005,2007,2009,2011,2013,2015),
                     labels = c(2005,2007,2009,2011,2013,2015))+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "Year",
       y = "Mean of Disordered Eating Symptoms",
       color = "Racial Identity", 
       caption = "Data from the National Health and Nutrition Examination Survey 2005-2015", 
       title = "Population Trends in Disordered Eating Symptoms Over 10 Years",
       subtitle = "by Racial Identity") +
  theme_minimal()
  
```


```{r raceplot3_draft, echo=TRUE}

race_plot <- race_weight_labeled %>%
  ggplot(aes(year, ed_mean_race)) +
  geom_point(aes(color = RIDRETH1), show.legend = F)+
  geom_line(aes(color = RIDRETH1), show.legend = F) +
  scale_x_continuous(breaks = c(2005,2007,2009,2011,2013,2015),
                     labels = c(2005,2007,2009,2011,2013,2015),
                     limits = c(2005,2017))+
  scale_y_continuous(labels = scales::percent,
                     limits = c(0.1,0.22))+
  labs(x = "Year",
       y = "Percentage of Sample Engagement \nin Disordered Eating Symptoms",
       color = "Racial Identity", 
       caption = "Data from the National Health and Nutrition Examination Survey 2005-2015", 
       title = "Population Trends in Disordered Eating Symptoms Over 10 Years",
       subtitle = "by Racial Identity") +
  geom_text_repel(data = filter(race_weight_labeled, year == "2015"),
            aes(y = ed_mean_race, label = RIDRETH1, color = RIDRETH1),show.legend = F,nudge_x = 300, segment.linetype = "dashed", segment.size = .2)+
  theme_minimal(base_size = 14) +
  theme(plot.caption = element_text(size = 10))+
  theme(axis.text=element_text(size=14))+
    theme(axis.title.y = 
          element_text(margin = 
                      margin(t = 0, r = 20, b = 0, l = 0)))


plotly::renderPlotly(race_plot)
```



```{r model1, echo=TRUE}
#testing model
race_weight$RIDRETH1<- as.factor(race_weight$RIDRETH1)  
race_weight <- race_weight %>%
  rowwise() %>%
  mutate(ed_mean = mean(ed_sum, na.rm = T))

ed_aov_race <- aov(ed_mean ~ RIDRETH1, data = race_weight)
summary(ed_aov_race)
TukeyHSD(ed_aov_race)
```



